---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# linearregtt

<!-- badges: start -->
<!-- badges: end -->

A simple linear regression function that fits a straight line to the data using the ordinary least squares method. It assumes that X and Y are numeric vectors of the same length and that X is not a constant vector. It returns a list of output similar to the lm function in R, containing the coefficients, standard errors, t-values, p-values, F-statistic, R-squared, adjusted R-squared, residuals, and fitted values.

## Installation

You can install the development version of linearregtt from [GitHub](https://github.com/) with:

```{r}
install.packages("devtools")
devtools::install_github("hrtang512/linearregtt")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(linearregtt)
## basic example 1
lmtt(c(1,2,3), c(0.9,1.8,3.1))

## basic example 2
X1 = c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
Y1 = c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
lmtt(X1,Y1)
```
